yield response function

### 2025-10-13 codes/R/visualized_results.qmd
CF YRF added
modified to include CF python

# --- Model name mapping ---
parse_model <- function(folder) {
  f <- str_to_lower(folder)

  case_when(
    str_detect(f, "^cf")          ~ "CF",
    str_detect(f, "^rann")        ~ "DO_ANN",
    str_detect(f, "^half_rann")   ~ "SO_ANN",
    str_detect(f, "^simple_ann")  ~ "No_ANN",
    str_detect(f, "^no_rf")       ~ "NO_RF",
    str_detect(f, "^halfrrf")     ~ "SO_RF",
    TRUE                          ~ NA_character_
  )
}

@@

read_eonr_file <- function(f) {
  obj <- read_any(f)
  if (is.list(obj) && all(c("pred","true") %in% names(obj))) {
    list(pred = as.numeric(obj$pred), true = as.numeric(obj$true))
  } else if (is.data.frame(obj) && all(c("pred","true") %in% names(obj))) {
    list(pred = as.numeric(obj$pred), true = as.numeric(obj$true))
  } else if (is.data.frame(obj) && all(c("opt_N_hat","opt_N") %in% names(obj))) {
    list(pred = as.numeric(obj$opt_N_hat), true = as.numeric(obj$opt_N))  # CF
  } else if (is.list(obj) && all(c("opt_N_hat","opt_N") %in% names(obj))) {
    list(pred = as.numeric(obj$opt_N_hat), true = as.numeric(obj$opt_N))  # CF list
  } else {
    stop("Unknown structure (need pred/true or opt_N_hat/opt_N): ", f)
  }
}

@@

  dirs <- fs::dir_ls(base_dir, type = "directory", recurse = FALSE) %>%
    keep(~ str_detect(basename(.x),
                      regex("^(cf|rann|half_rann|simple_ann|no_rf|halfrrf)",
                            ignore_case = TRUE)))

@@

```{r}
# ---- run it (all models) ----
rmse_tbl_raw <- build_rmse_table(
  base_dir = here("results"),
  expected_rows = EXPECTED_ROWS
)

# save
# write_csv(rmse_tbl_raw, here("results", "rmse_table_all_models.csv"))
#saveRDS(rmse_tbl_raw, here("results", "rmse_tbl_raw.rds"))

@@

# -- labels for models ---
model_names <- function(models) {
  map <- c(
    "Simple_ANN" = "No_ANN",
    "RANN"       = "DO_ANN",
    "NO_RF"      = "NO_RF",
    "HALFRANN"   = "SO_ANN",
    "HALFRRF"    = "SO_RF",
    "CF"         = "CF"
  )
  # use mapping if available, else leave unchanged
  out <- unname(map[models])
  ifelse(is.na(out), models, out)
}

# --- plotting data ---
rmse_plot_df <- rmse_tbl_raw %>%
  filter(ok_rows) %>%
  mutate(
    row_lab = model_names(Model),
    col_lab = factor(
      `#field`,
      levels = sort(unique(`#field`)),   # discover field counts
      labels = paste0("Number of fields: ", sort(unique(`#field`)))
    )
  )

# --- Check ---
rmse_plot_df %>% count(row_lab, col_lab)

# ------
xmin <- 0
nice_ceiling <- function(x, base = 5) base * ceiling(x / base)
xmax <- nice_ceiling(max(rmse_plot_df$RMSE, na.rm = TRUE), base = 5)

@@

# --- Plot ---
p <- ggplot(rmse_plot_df, aes(x = RMSE)) +
  geom_histogram(binwidth = binwidth, boundary = 0, closed = "left") +
  facet_grid(row_lab ~ col_lab, scales = "fixed") +  
  scale_x_continuous(
    limits = c(xmin, xmax),
    breaks = seq(xmin, xmax, length.out = 6),
    expand = c(0, 0)
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(x = "RMSE by iteration", y = "Count") +
  theme_bw() +
  theme(
    strip.text = element_text(face = "bold", size = 16),
    axis.title = element_text(size = 14)
  )

p
# ggsave(here::here("results", "rmse_hist_3rows.png"), p, width = 12, height = 7, dpi = 300)

@@

>>>>

# --- model name mapping ---
parse_model <- function(folder) {
  f <- str_to_lower(folder)

  case_when(
    str_detect(f, "^cf_python")     ~ "CF_Python",
    str_detect(f, "^cf")            ~ "CF",
    str_detect(f, "^rann")          ~ "DO_ANN",
    str_detect(f, "^half_rann")     ~ "SO_ANN",
    str_detect(f, "^simple_ann")    ~ "No_ANN",
    str_detect(f, "^no_rf")         ~ "NO_RF",
    str_detect(f, "^halfrrf")       ~ "SO_RF",
    TRUE                            ~ NA_character_
  )
}

@@

read_eonr_file <- function(f) {
  obj <- read_any(f)
  if (is.data.frame(obj) && all(c("opt_N_hat","opt_N") %in% names(obj))) {
    list(pred = as.numeric(obj$opt_N_hat), true = as.numeric(obj$opt_N))  # CF or CF_python csv
  } else if (is.list(obj) && all(c("opt_N_hat","opt_N") %in% names(obj))) {
    list(pred = as.numeric(obj$opt_N_hat), true = as.numeric(obj$opt_N))
  } else if (is.data.frame(obj) && all(c("pred","true") %in% names(obj))) {
    list(pred = as.numeric(obj$pred), true = as.numeric(obj$true))
  } else {
    stop("Unknown structure (need pred/true or opt_N_hat/opt_N): ", f)
  }
}

@@

  dirs <- fs::dir_ls(base_dir, type = "directory", recurse = FALSE) %>%
    keep(~ str_detect(basename(.x),
                      regex("^(cf|cf_python|rann|half_rann|simple_ann|no_rf|halfrrf)",
                            ignore_case = TRUE)))

@@

```{r}
# ---- run it (all models) ----
rmse_tbl_raw <- build_rmse_table(
  base_dir = here("results"),
  expected_rows = EXPECTED_ROWS
)
# save
# write_csv(rmse_tbl_raw, here("results", "rmse_table_all_models.csv"))
#saveRDS(rmse_tbl_raw, here("results", "rmse_tbl_raw.rds"))

@@

# -- label mapping for models ---
model_names <- function(models) {
  map <- c(
    "Simple_ANN" = "No_ANN",
    "RANN"       = "DO_ANN",
    "HALFRANN"   = "SO_ANN",
    "HALFRRF"    = "SO_RF",
    "NO_RF"      = "NO_RF",
    "CF"         = "CF",
    "CF_Python"  = "CF_Python"
  )

  # normalize capitalization 
  models_upper <- toupper(models)
  out <- map[models_upper]
  ifelse(is.na(out), models, out)
}

# ---  data for plotting ---
rmse_plot_df <- rmse_tbl_raw %>%
  filter(ok_rows) %>%
  mutate(
    row_lab = model_names(Model),
    col_lab = factor(
      `#field`,
      levels = sort(unique(`#field`)),
      labels = paste0("Number of fields: ", sort(unique(`#field`)))
    )
  )

# ---number of sims per facet ---
rmse_plot_df %>% count(row_lab, col_lab)

# --- axis ranges ---
xmin <- 0
nice_ceiling <- function(x, base = 5) base * ceiling(x / base)
xmax <- nice_ceiling(max(rmse_plot_df$RMSE, na.rm = TRUE), base = 5)

@@

# --- Plot ---
p <- ggplot(rmse_plot_df, aes(x = RMSE)) +
  geom_histogram(binwidth = binwidth, boundary = 0, closed = "left", fill = "skyblue3") +
  facet_grid(row_lab ~ col_lab, scales = "fixed") +
  scale_x_continuous(
    limits = c(xmin, xmax),
    breaks = seq(xmin, xmax, length.out = 6),
    expand = c(0, 0)
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(
    title = "distribution of RMSE across models and field counts",
    x = "RMSE by iteration",
    y = "Count"
  ) +
  theme_bw() +
  theme(
    strip.text = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 13),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16)
  )

p

# ggsave(here::here("results", "rmse_hist_3rows.png"), p, width = 12, height = 7, dpi = 300)

@@

# YRF for CF

```{r}
all_plots <- readRDS(here::here("results/yield_response_function_for_one_iteration", "all_YRF_plots_CF.rds"))

# Example one plot
#all_plots[[1]]

# arrange 
wrap_plots(all_plots, ncol = 2)
